### 2014-07-28 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago report: Fix typo

While the food failure time needed to be estimated, the important detail is that after the door failed, an interior flow path from the enclosed porch to the kitchen of the structure was created. This resulted in a rapid change in the conditions within the flow path. The combustion gases at elevated temperature and pressure in the enclosed porch were vented by the failure of the door to lower pressure areas in the hallways and kitchen, where the conditions seemed to equilibrate. The arrows in Fig.~(\ref{fig:flowpath_1}) show the flow direction of gases on the second floor following the door failure.

>>>>

While the door failure time needed to be estimated, the important detail is that after the door failed, an interior flow path from the enclosed porch to the kitchen of the structure was created. This resulted in a rapid change in the conditions within the flow path. The combustion gases at elevated temperature and pressure in the enclosed porch were vented by the failure of the door to lower pressure areas in the hallways and kitchen, where the conditions seemed to equilibrate. The arrows in Fig.~(\ref{fig:flowpath_1}) show the flow direction of gases on the second floor following the door failure.
